A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-19 tex/body.tex
more

To evaluate the decision procedure, we generated benchmark problems from existing
Isabelle formalizations using Sledgehammer.
Codatatypes being a recent addition to Isabelle
\cite{blanchette-et-al-2014-impl}, benchmarks are not abundant. We
included all the theory files from the Isabelle distribution (Distro, 879 goals)
and the \emph{Archive of Formal Proofs} (AFP, 2974 goals) \cite{klein-et-al-afp}
that define codatatypes falling within the supported fragment. We also included
two unpublished theories by Peter Gammie and Andreas Lochbihler (\gandl, 317
goals), about Bird and Stern--Brocot trees. To exercise the support
for datatypes, the benchmarks are complemented by theories about lists
and trees. The theories were selected before running the
experiments. The experimental data are publicly available.%
\footnote{\url{http://www21.in.tum.de/~blanchet/codp_data.tgz}}

@@

\begin{table*}[t!]
\normalsize
\begin{center}\begin{tabular}{@{\;}l@{\kern1.5em}cc@{\kern.5em}cc@{\kern.5em}cc@{\kern1.3em}cc@{\;}}
  & \multicolumn{2}{c}{Distro} & \multicolumn{2}{c}{AFP} & \multicolumn{2}{c}{\gandl} & \multicolumn{2}{c}{Overall} \\
  & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4}
\MIDRULE
No (co)datatypes
  & 209 & 221 & 777 & 775 & \phantom{0}51 & \phantom{0}52 & 1037 & 1048 \\%[\jot]
%Datatype simplication only
%  &  \\
Datatypes w/o \rn{Acyclic}
  & & 227 & & 780 & & \phantom{0}52 & & 1059 \\
Full datatypes
  & 213 & 227 & 791 & 786 & \phantom{0}51 & \phantom{0}52 & 1055 & 1065 \\%[\jot]
%Codatatype simplication only
%  &  \\
Codatatypes w/o \rn{Unique}
  & & 222 & & 804 & & \phantom{0}56 & & 1082 \\
Full codatatypes
  & & 223 & & 804 & & \bfseries \phantom{0}59 & & 1086 \\%[\jot]
Full (co)datatypes
  & & \bfseries 229 & & \bfseries 815 & & \bfseries \phantom{0}59 & & \bfseries 1103% \\[\jot]
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}

>>>>

To evaluate the decision procedure, we generated benchmark problems from existing
Isabelle formalizations using Sledgehammer.
Codatatypes being a recent addition to Isabelle
\cite{blanchette-et-al-2014-impl}, benchmarks are not abundant. We
included all the theory files from the Isabelle distribution (Distro, 879 goals)
and the \emph{Archive of Formal Proofs} (AFP, 2974 goals) \cite{klein-et-al-afp}
that define codatatypes falling within the supported fragment. We also included
two unpublished theories by Peter Gammie and Andreas Lochbihler (\gandl, 317
goals), about Bird and Stern--Brocot trees. To exercise the support
for datatypes, the benchmarks were complemented by theories about lists
and trees. The theories were selected before running the
experiments. The experimental data are publicly available.%
\footnote{\url{http://www21.in.tum.de/~blanchet/codp_data.tgz}}

@@

\begin{table*}[t!]
\normalsize
\begin{center}\begin{tabular}{@{\;}l@{\kern1.5em}cc@{\kern.5em}cc@{\kern.5em}cc@{\kern1.3em}cc@{\;}}
  & \multicolumn{2}{c}{Distro} & \multicolumn{2}{c}{AFP} & \multicolumn{2}{c}{\gandl} & \multicolumn{2}{c}{Overall} \\
  & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4} & \HD{Z3} & \HD{CVC4}
\MIDRULE
No (co)datatypes
  & 209 & 221 & 777 & 775 & 51 & 52 & 1037 & 1048 \\%[\jot]
%Datatype simplication only
%  &  \\
Datatypes w/o \rn{Acyclic}
  & -- & 227 & -- & 780 & -- & 52 & -- & 1059 \\
Full datatypes
  & 213 & 227 & 791 & 786 & 51 & 52 & 1055 & 1065 \\%[\jot]
%Codatatype simplication only
%  &  \\
Codatatypes w/o \rn{Unique}
  & -- & 222 & -- & 804 & -- & 56 & -- & 1082 \\
Full codatatypes
  & -- & 223 & -- & 804 & -- & \bfseries 59 & -- & 1086 \\%[\jot]
Full (co)datatypes
  & -- & \bfseries 229 & -- & \bfseries 815 & -- & \bfseries 59 & -- & \bfseries 1103% \\[\jot]
\end{tabular}\end{center}
\caption{\,Number of solved goals for the three benchmark suites}
\label{tab:bench}
\end{table*}
